Dynamic Walking and Whole-Body Motion Planning for Humanoid Robots: an Integrated Approach

### 2012-12-05 paper.tex
Update and add computation times.

The environment shown in Fig. \ref{fig:couv} and \ref{fig:sliding} was presented
in \cite{el2011path}. There, the motion planning problem is solved with a bounding
box method, leading the robot to walk sideways between the two chairs.
Our method generates a locomotion  trajectory in which the robot walks
forward, which may be required if the robot has to use vision during
locomotion. The first planning stage  requires 29.6~s
on  average.   The  animation  of   the  sliding  path   presented  in
Fig.   \ref{fig:sliding}   uses  66.5~s  of  computation   time.

@@

In the environment shown in Fig. \ref{fig:cluttered}, the robot
has to find a way among floating obstacles. In this
environment neither bounding box nor footstep planning strategies
could find a collision-free walk trajectory.
The first planning stage requires
184.3~s on average, and the animation of the trajectory presented in 
Fig.~\ref{fig:cluttered} uses 339.5~s of computation time. Fig.~\ref{fig:cluttered-waist} 
shows the robot CoM trajectory during locomotion.

@@

Fig.~\ref{fig:shelf} shows the resulting walk motion and Fig.~\ref{fig:shelf-waist} 
shows the robot CoM trajectory during locomotion. Extension 3 presents a 
comprehensive video of this problem, including the motion execution on
the real robot HRP-2 on stage. Fig.~\ref{fig:shelf-cdf} shows some snapshots 
taken from Extension 3.

>>>>

The environment shown in Fig. \ref{fig:couv} and \ref{fig:sliding} was presented
in \cite{el2011path}. There, the motion planning problem is solved with a bounding
box method, leading the robot to walk sideways between the two chairs.
Our method generates a locomotion  trajectory in which the robot walks
forward, which may be required if the robot has to use vision during
locomotion. The first planning stage  requires 1~s
on  average.   The  animation  of   the  sliding  path   presented  in
Fig.   \ref{fig:sliding}   uses  66.5~s  of  computation   time.

@@

In the environment shown in Fig. \ref{fig:cluttered}, the robot
has to find a way among floating obstacles. In this
environment neither bounding box nor footstep planning strategies
could find a collision-free walk trajectory.
The first planning stage requires
53~s on average, and the animation of the trajectory presented in 
Fig.~\ref{fig:cluttered} uses 339.5~s of computation time. Fig.~\ref{fig:cluttered-waist} 
shows the robot CoM trajectory during locomotion.

@@

\textbf{The first planning stage requires 15~s on average, and the
  animation of the resulting walk motion presented in
  Fig.~\ref{fig:shelf} requires around 190~s of computation time.}
Fig.~\ref{fig:shelf-waist} shows the robot CoM trajectory during
locomotion. Extension 3 presents a comprehensive video of this
problem, including the motion execution on the real robot HRP-2 on
stage. Fig.~\ref{fig:shelf-cdf} shows some snapshots taken from
Extension 3.
